Title-Data Visualisation-DS241
Author-Demetrius Boone

Before you begin there are a few cruical steps that you must do, You need
to ensure that you are able to use the needed functions to create certain
visualisations (scatterplot, histogram, barchart, lineplot).

First installing and applying the packages associated by using:
```{r}
library(tidyverse)
library(readxl)
library(plotly)
library(janitor)
library(readxl)
library(skimr)
library(summarytools)
```
  
Next step is to obtain a data set and prepare it for use, for this case a sample
data set will be used from R but any data set will work, you can choose any data
from the list you generate but running the following code:

```{r}
data()
```

### Choosing the data

For this example however i will be using data from the world bank and showing population data
(found here https://data.worldbank.org/indicator/SP.POP.TOTL?locations=AF):

```{r}
dfa = read_excel("~/Rstudio work/Population.xlsx") %>% clean_names() 
```


```{r}
skim(dfa)
```
### Visualzing the data

Next you cant show all 264 countrys at once and it be somewhat pleasing this is where
random sliceing comes from and helps show data to a smaller degree:

```{r}
dfa1=dfa %>% slice_sample(n=10)
```

Then you can form a proper graph using the sliced data to show a population of
whatever year you want to find:
```{r}
ggplot(data = dfa1, aes(x = country_code, y = x1962)) + geom_point()
```
### Editing the Data Frame

Pivot longer allows you to join data properly if you have a list of data that 
needs to go from being rows to its own col:
```{r}
dfa2=pivot_longer(dfa1, starts_with("x"), names_to = "year")
```

After you must rename the new col so someone who looks at the new list will 
understand:
```{r}
dfa3= rename(dfa2,"population " ="value")
```

Now you can break up each dataset into its proper country that you would want to analyze:
```{r}
dfa4= filter(dfa3, country_code== "IMN")
```




